Results

### 2024-05-15 Analysis/04_Summarise_results.Rmd
Removed raos and reorder metrics

## Re-ordering results for fancyness
new_order <- c(14, 12, 3, 6,
               15, 11, 2, 8,
               7, 4, #5,
               13,
               10, 9, 1)
all_results_2d <- lapply(all_results_2d, sort.metrics, order = new_order)
all_results_3d <- lapply(all_results_3d, sort.metrics, order = new_order)
all_results_4d <- lapply(all_results_4d, sort.metrics, order = new_order)
all_results_5d <- lapply(all_results_5d, sort.metrics, order = new_order)
all_results_8d <- lapply(all_results_8d, sort.metrics, order = new_order)
empirical_results <- lapply(empirical_results, sort.metrics, order = new_order)

@@

## Fancier names
fancy_names <- rev(
               c("Functional evenness\nprobability density\nTPD::REND",
                 "Functional evenness\nhypervolume\nBAT::kernel.evenness",
                 "Functional evenness\ndendrogram\nBAT::evenness",
                 "Functional evenness\ndistances\nFD::dbFD()$FEve",
                 "Divergence\nprobability density\nTPD::REND",             
                 "Functional dispersion\nhypervolume\nBAT::kernel.dispersion",
                 "Functional dispersion\ndendrogram\nBAT::dispersion",
                 "Melodic Mean Pairwise Distance\ndistances\nmelodic.rao",
                 "Melodic Rao\ndistances\nmelodic.rao",
                 "Rao's quadratic entropy\ndistances\nFD::dbFD()$RaoQ",
                 #"dissimilarity[FD]\ndivergence",
                 "Functional richness\nprobability density\nTPD::REND",
                 "Functional richness\nhypervolume\nBAT::kernel.alpha",
                 "Functional richness\nconvex hull\nBAT::hull.alpha",
                 "Alpha diversity\ndendrogram\nBAT::alpha"))
```

@@

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
col_vector <- c(rep("blue", 4), # The richness ones
                rep("orange", 6), # The divergence ones
                rep("darkgreen", 4)) # The regularity ones
## The plot
fancy.plot(scaled_results_2d, col = col_vector, lm = model_fits_2d, null = null_differences_2d, metric.names = fancy_names, pch = rep(19,4))

>>>>

## Re-ordering results for fancyness
new_order <- c(# Richness
               13, 10, 9, 1,
               # Divergence
               15, 11, 2, #8,
               #7,
               4, #5,
               # Regularity
               14, 12, 3, 6)

all_results_2d <- lapply(all_results_2d, sort.metrics, order = new_order)
all_results_3d <- lapply(all_results_3d, sort.metrics, order = new_order)
all_results_4d <- lapply(all_results_4d, sort.metrics, order = new_order)
all_results_5d <- lapply(all_results_5d, sort.metrics, order = new_order)
all_results_8d <- lapply(all_results_8d, sort.metrics, order = new_order)
empirical_results <- lapply(empirical_results, sort.metrics, order = new_order)

@@

## Fancier names
fancy_names <- rev(
               c(
                 "Functional richness\nprobability density\nTPD::REND",
                 "Functional richness\nhypervolume\nBAT::kernel.alpha",
                 "Functional richness\nconvex hull\nBAT::hull.alpha",
                 "Alpha diversity\ndendrogram\nBAT::alpha",

                 "Divergence\nprobability density\nTPD::REND",             
                 "Functional dispersion\nhypervolume\nBAT::kernel.dispersion",
                 "Functional dispersion\ndendrogram\nBAT::dispersion",
                 #"Melodic Mean Pairwise Distance\ndistances\nmelodic.rao",
                 #"Melodic Rao\ndistances\nmelodic.rao",
                 "Rao's quadratic entropy\ndistances\nFD::dbFD()$RaoQ",
                 #"dissimilarity[FD]\ndivergence",

                 "Functional evenness\nprobability density\nTPD::REND",
                 "Functional evenness\nhypervolume\nBAT::kernel.evenness",
                 "Functional evenness\ndendrogram\nBAT::evenness",
                 "Functional evenness\ndistances\nFD::dbFD()$FEve"
               ))
```

@@

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
col_vector <- c(rep("darkgreen", 4), # The regularity ones
                rep("orange", 4), # The divergence ones
                rep("blue", 4)) # The richness ones
## The plot
fancy.plot(scaled_results_2d, col = col_vector, lm = model_fits_2d, null = null_differences_2d, metric.names = fancy_names, pch = rep(19,4))
